Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-16 paper.tex
fixes

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example,838,663,683,
b,bids/freesurfer,353,215,192,
c,bids/ndmg,934,757,782,
d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection,1086,849,868,
f,bids/spm,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no oval data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc,67,16,no oval data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textcolor{red}{mcin/qeeg:latest},46,46,142,
ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest},70,76,157,
ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest},70,76,157,
ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textcolor{red}{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

Today, containers, which provide operating system level virtualization, are
popular. Correspondingly, they are widely used for scientific data analyses on 
High Performance Computing (HPC) clusters. However, the security of containers
still remains the concerning issue. Here, we focus on the security of container
images in particular. Container images are often built for the entire
duration of an analysis, so scientific researchers do not prefer to update
them. Consequently, their chances of containing vulnerabilities increases.  
In this study, we analyze vulnerabilities in container images used in 
HPC clusters.
We conduct two different
experiments, image update and image minimization, to report the effect 
on the number of vulnerabilities.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources, which are listed in the Table~\ref{database}.
%from the Open Vulnerability
%and Assessment Language (OVAL) database 
According to this list, Vuls
refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

BIDS app and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

@@

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

Following the above two approaches, we employ a hybrid approach, where
we combine both update and size reduction processes in an attempt to
lessen number of vulnerabilities or to test the effect of
combining two approaches. To allow for that, we first update all packages
the image, then delete all unnecessary packages. Applying these processes in reverse
may reduce the needed work; however this is not possible in all cases. For instance,
some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
ahead of time will disallow the update process to take place.
%Finally, we combine both update and size reduction process
%to lessen the number of vulnerabilities.
%Therefore, in this process we first update all the packages in the image and then deletes
%the unnecessary packages. For this process we used the same scripts that
%we used for earlier experiments.
%\begin{comment}
%\subsection{CBRAIN}
%
%\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
%used for the processing of distributed data on various storage locations of computing
%clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
%delivered by Compute Canada~\cite{das2016mni}.
%It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
%neuroimaging research platform that is active in production since 2009. CBRAIN
%provides transparent access to various distributed storage sites and computing
%resources across the world. CBRAIN’s infrastructure consists of three main
%layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
%layer is for CBRAIN users, and can be accessed through any modern browser or
%RESTful API. The service layer consists of CBRAIN portal, which contains
%metadata and databases. It provides information about users, their permissions,
%resources etc. The infrastructure layer consists of data resources and computing
%resources, which are connected through a network. 
%CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
%CBRAIN users uses a portal
%account on the cluster. Users are only able to
%run pre-defined applications on the cluster through the CBRAIN portal.
%\end{comment}
\section{Results}

In this section,
we first discuss our detected vulnerabilities in the images, using the three scanners, and compare the
results. We then discuss the effect of the image updating/minimizing and applying the hybrid
approach on the detected vulnerabilities.
Lastly, we do an analysis of obtained results and explain the reasons behind our
findings.

@@

Table~\ref{table1} shows the number of detected vulnerabilities in the different images,
detected by each of the scanners.
Interestingly, our experiments concluded considerable discrepancies in the results obtained by
these scanners. In particular, in most cases,
Anchore reports more vulnerabilities than Vuls and Clair-scanner resulting in 
the Jaccard coefficient of 0.59 with both,
whereas Vuls and Clair-scanner share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.

>>>>

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example:latest,838,663,683,
b,bids/freesurfer:latest,353,215,192,
c,bids/ndmg:latest,934,757,782,
d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection:latest,1086,849,868,
f,bids/spm:latest,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment:latest,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome:latest,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak:latest,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm:latest,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain:latest,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus:latest,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no OVAL data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc:latest,67,16,no OVAL data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textcolor{red}{mcin/qeeg:latest},46,46,142,
ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textcolor{red}{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

Today, containers, which provide operating system level virtualization, are
popular. Correspondingly, they are widely used for scientific data analyses on 
High Performance Computing (HPC) clusters. However, the security of containers
still remains a concerning issue. Here, we focus on the security of container
images, which are often built for the entire
duration of an analysis, so scientific researchers prefer not to update
them. Consequently, their chances of containing vulnerabilities increases.  
In this study, we analyze vulnerabilities in container images used in 
HPC clusters.
We conduct two different
experiments, image update and image minimization, to report the effect 
on the number of vulnerabilities.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources, which are listed in the Table~\ref{database}.
%from the Open Vulnerability
%and Assessment Language (OVAL) database 
According to this list, Vuls
refers to Open Vulnerability and Assessment Language (OVAL) database for some distribution e.g. Ubuntu, Debian, etc.
It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

BIDS apps and Boutiques images in our experiments have diverse Linux
distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

@@

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, an open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

Following the two previous approaches, we employ a hybrid approach, where
we combine both update and size reduction processes in an attempt to
lessen number of vulnerabilities or to test the effect of
combining two approaches. To allow for that, we first update all packages in
the image, then delete all unnecessary packages. Applying these processes in reverse
may reduce the needed work; however this is not possible in all cases. For instance,
some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
ahead of time will disallow the update process to take place.
%Finally, we combine both update and size reduction process
%to lessen the number of vulnerabilities.
%Therefore, in this process we first update all the packages in the image and then deletes
%the unnecessary packages. For this process we used the same scripts that
%we used for earlier experiments.
%\begin{comment}
%\subsection{CBRAIN}
%
%\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
%used for the processing of distributed data on various storage locations of computing
%clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
%delivered by Compute Canada~\cite{das2016mni}.
%It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
%neuroimaging research platform that is active in production since 2009. CBRAIN
%provides transparent access to various distributed storage sites and computing
%resources across the world. CBRAIN’s infrastructure consists of three main
%layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
%layer is for CBRAIN users, and can be accessed through any modern browser or
%RESTful API. The service layer consists of CBRAIN portal, which contains
%metadata and databases. It provides information about users, their permissions,
%resources etc. The infrastructure layer consists of data resources and computing
%resources, which are connected through a network. 
%CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
%CBRAIN users uses a portal
%account on the cluster. Users are only able to
%run pre-defined applications on the cluster through the CBRAIN portal.
%\end{comment}
\section{Results}

In this section,
we first discuss the detected vulnerabilities in the images and compare the
results. We then discuss the effect of updating/minimizing the image and applying the hybrid
approach on the detected vulnerabilities.
Lastly, we do an analysis of obtained results and explain the reasons behind our
findings.

@@

Table~\ref{table1} shows the number of detected vulnerabilities in the different images,
detected by each of the scanners. Image labels from \texttt{a} to \texttt{al} represents
Docker images, whereas remaining ones belong to Singularity. It is worth noting that Vuls
is not able to scan two Docker images \textttt{w} and \textttt{y} because these images
have Ubuntu 17.04 and 17.10 respectively, and there is no vulnerability data for these
distributions in OVAL database, which Vuls refers for scanning. 
Interestingly, our experiments concluded considerable discrepancies in the results obtained by
these scanners. In particular, in most cases,
Anchore reports more vulnerabilities than Vuls and Clair-scanner resulting in 
the Jaccard coefficient of 0.59 with both,
whereas Vuls and Clair-scanner share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
